---
title: "DicoExpress interactif"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
date: "2024-06-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

n
# Intro

give working directory path

```{r set working directory}
setwd("d:/Users/Gabriel/Documents/travail/ENSL/satge/EXP/dicoexpress")
print(getwd())  
# Vérifiez le répertoire de travail actuel
source_path = "Sources_v2/"
file_path = paste0(source_path, "Load_Functions.R")

if (file.exists(file_path)) {
  source(file_path)
} else {
  stop("Le fichier Load_Functions.R n'existe pas dans le chemin spécifié.")
}


Data_Directory = "./Data"
Results_Directory = "./Results"
Project_Name = "EXP3"
```

load functions

```{r load functions, echo=FALSE, message=FALSE}
Load_Functions(source_path)
```

# Data importation

transform Salmon output in DicoExpress readable format

```{r clean row names, message= F}
clean_row_names(Data_Directory, Project_Name, "EXP3_Salmon_quant.sf")
```

transform xlx into TARGET file

```{r echo=F}
input_file = "Expe3_ANR_Compilation_081123 (1).xlsx"
sample_list = "sample_list_2.txt"

create_target_file(Data_Directory, Project_Name, input_file, sample_list)

```

set parameters

```{r}
Filter = NULL
Sep = ","
```

load data

```{r}
Data_Files = Load_Data_Files(Data_Directory, Project_Name, Filter, Sep)

Project_Name = Data_Files$Project_Name
Target = Data_Files$Target
Raw_Counts = Data_Files$Raw_Counts 
Annotation = Data_Files$Annotation 
Reference_Enrichment = Data_Files$Reference_Enrichment

Filter_Counts <- Raw_Counts %>% 
  dplyr::select(-RD_106_B)

Filter_Target <- Target %>% 
  filter(!row.names(Target)== "RD_106_B")
```

# Quality Control

set parameters

```{r}
Color_Group =  NULL
min.count = 30
Normalization_Method = "TMM"
Filter_Strategy = "filterByExpr"

#number of marginal sample to display
marginal_sample = 10
```

launch QC

```{r}
Load_Functions(source_path)

Quality_Control(Data_Directory, Results_Directory, Project_Name, Filter_Target,
                Filter_Counts, Color_Group,Min.count=min.count,Normalization_Method,marginal_sample)
```

# Statistical model

param

```{r}
Replicate = TRUE
Interaction = TRUE
```

launch

```{r}
Model = GLM_Contrasts(Results_Directory, Project_Name, Filter_Target, Replicate, Interaction)
GLM_Model = Model$GLM_Model
Contrasts = Model$Contrasts
```

# Differential Analysis

param

```{r}
Alpha_DiffAnalysis = 0.05
Index_Contrast = 1:29
NbGenes_Profiles = 20
NbGenes_Clustering = 50
min.count = 30
Normalization_Method = "TMM"
```

launch

```{r}
DiffAnalysis.edgeR(Data_Directory, Results_Directory, Project_Name,
                   Filter_Target, Filter_Counts, GLM_Model, Contrasts, Index_Contrast
                   , Alpha_DiffAnalysis, NbGenes_Profiles,
                   NbGenes_Clustering, min.count, Normalization_Method)
```

# DEGs Enrichment

```{r}
Alpha_Enrichment = 0.05
Title=NULL
Enrichment(Results_Directory, Project_Name, Title, Reference_Enrichment, Alpha_Enrichment)
```

# Contrast Comparison

param

```{r}
Title="infected_comparison"
Groups_Contrast_Comparison = Contrasts$Contrasts[14:19]
Operation="Union"
```

launch

```{r}
Contrast_Comparison(Data_Directory, Results_Directory, Project_Name, Title, Groups_Contrast_Comparison, Operation)
```

launch as a loop

```{r}
for (i in 1:5){
  Contrast_Comparison(Data_Directory, Results_Directory, Project_Name, paste("Interaction with Genotypes",as.character(10*i+7),"to",as.character(10*(i+1))),
                    Contrasts$Contrasts[10*i+7:10*(i+1)], "Union")
}
```

# Co-expression

```{r}
Title="Interaction_with_Genotypes_1_and_2"
Groups_Coexpression = Contrasts$Contrasts[1:2]
Operation="Union"
meanFilterCutoff=50
```

```{r}
Coexpression_coseq(Data_Directory, Results_Directory, Project_Name, Title, Groups_Coexpression,Operation, Target, Raw_Counts,Color_Group=NULL,meanFilterCutoff)
```

# Cluster Enrichment

```{r}
Title="Interaction_with_Genotypes_1_and_2"
Alpha_Enrichment = 0.05
```

```{r}
Enrichment(Results_Directory, Project_Name, Title, Reference_Enrichment, Alpha_Enrichment)
```

# Save parameters and cluster version

```{r}
Save_Parameters()
```
